Names diffusion and social class

### 2024-02-16 text/paper.tex

>>>>

\begin{landscape}
\begin{figure}[H]
\begin{center}
    \includegraphics[width=22cm]{plot/top_quintil_1.png}
    \caption{Top nombre por quintil por año}
    \label{fig:top_quintil_1}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[H]
\begin{center}
    \includegraphics[width=22cm]{plot/top_quintil_2.png}
    \caption{Top nombre por quintil por año}
    \label{fig:top_quintil_2}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[H]
\begin{center}
    \includegraphics[width=22cm]{plot/top_quintil_3.png}
    \caption{Top nombre por quintil por año}
    \label{fig:top_quintil_3}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[H]
\begin{center}
    \includegraphics[width=22cm]{plot/top_quintil_4.png}
    \caption{Top nombre por quintil por año}
    \label{fig:top_quintil_4}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}[H]
\begin{center}
    \includegraphics[width=22cm]{plot/top_quintil_5.png}
    \caption{Top nombre por quintil por año}
    \label{fig:top_quintil_5}
\end{center}
\end{figure}
\end{landscape}
